%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a sample header for a sample dissertation. Fill in the name,
% and the other information. LaTeX will work out the table of
% content, the list of figures and of tables for you.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\thispagestyle{empty}

% ******* Title page *******
% **************************

\vspace*{2cm}
\begin{center}
{\Large\bf Acquisition of 3D tennis ball trajectory and velocity from monocular vision systems\\} \vspace{2cm} {\large
Vujovic Dragutin\\
\vspace{2cm}
Department of Computer Architecture and Technology \\
University of Girona}

\end{center}

\vspace{7cm}
\begin{center}
{\large A Thesis Submitted for the Degree of \\MSc Erasmus Mundus
in Vision and Robotics (VIBOT) \\\vspace{0.3cm} $\cdot$ 2016
$\cdot$}
\end{center}
\singlespacing


%ABSTRACT
\begin{abstract}
Video annotations are successfully used in many sport related areas, including training, the media coverage and sport science. The key advantages of automatic annotation over conventional manual are speed, and robustness of gathered data. However, current automatic annotations systems are not always practical due installation cost and media rights. The proposed solution provides this kind of data from broadcast videos and single camera shots.\\

The main contribution of this work is acquisition of 3D trajectory and velocity of tennis ball, including players’ positions. The 3D trajectory acquisition is based on ball detection, field lines recognition and prior information about field dimension. The accuracy is tested on all four Grand Slam tournament matches, by available ground-truth data.

\vspace*{5cm}



\begin{center}
\begin{quote}
\it Research is what I'm doing when I don't know what I'm
doing.\,\ldots
\end{quote}
\end{center}
\hfill{\small Werner von Braun}

\end{abstract}

\doublespacing

%\pagestyle{empty}
\pagenumbering{roman}
\setcounter{page}{1} \pagestyle{plain}


\tableofcontents

\listoffigures
\listoftables

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}
         {\protect\numberline{Acknowledgments\hspace{-96pt}}}

I would like to express deep gratitude to many people who provide support, time, and effort to make this thesis possible. First of all, to VIBOT staff for unselfish and exceptional support and understanding during whole master course. Secondly, to Aalborg university for perfect conditions, expertise and support which transformed simple idea into this master thesis. Last but not least, I would like to express gratitude to friends and family for their unique support.

\pagestyle{fancy}
